Approximate State Abstraction

### 2015-12-03 paper/approximate_state_abstraction.tex
Outline updated

% --- Note Commands ---
\usepackage{color}
\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
\newcommand\ellisnote[1]{\textcolor{red}{Ellis: #1}}

@@

@@

@@

% --- SECTION: State Abstraction ---
\section{State Abstraction}

% --- SECTION: Preserving Optimality ---
\section{Preserving Optimality}

@@

@@

>>>>

% --- Note Commands ---
\usepackage{color}
\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}

@@

\begin{itemize}
\item Solving MDPs is P-Complete, where the dominant factor is $|\mathcal{S}|$.
\item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
\item So, in order to make MDPs with large $|\mathcal{S}|$ tractable, we can reduce them to a simpler form.
\item In this work we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
\item Q: Why approximate?
\item A: Approximate can compress strictly more than compression based on equality
\item A: Approximate compression requires the type of knowledge that we could imagine learning (i.e.. approximate knowledge)
\end{itemize}

@@

% Quick MDP blurb

% Previous state aggregation stuff?

@@

% Lihong

% Nan/Lihong

% Approximate bisimulation

% Other folks...

% --- SECTION: State Abstraction ---
\section{Approximate State Abstraction}

% Explain each of the Phi's
% Subsections for proofs for each phi
\dnote{Insert lemma for each phi as their subsection}

% Subsection: Phi_M
\subsection{$\Phi_M$}

% Subsection: Phi_Q
\subsection{$\Phi_Q^*$}

% Subsection: Phi_D
\subsection{$\Phi_D$}

% Subsection: Other Abstractions
\subsection{Other Abstractions}

@@

\subsection{UpWorld}

\dnote{As part of upworld we can include the result about the unbounded improvement in sample complexity}

% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP

\subsection{NChain}

% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP

\subsection{Trench}

% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP

@@

% Summary

% Future Work
\begin{enumerate}
\item Learning Phi
\begin{itemize}
\item Exploration vs. Exploitation problem is different while trying to learn Phi
\end{itemize}
\item Compressibility
\begin{itemize}
\item Relationship between approximate abstract and compressibility
\end{itemize}
\item 
\end{enumerate}
